B\'{e}zier $\bar{B}$ projection

### 2018-01-26 projection1120.tex
Revisions.

\added{Contour plots of  $\sigma_{xx}$ for biquartic elements of the finest mesh are shown in Figure \ref{fig:platewithhole_contour}. We denote that, for the finest mesh, results from all $\bar{B}$ methods are consistent with the refernce solution, while using standard finite element still leads to a huge error. Figure \ref{fig:platewithhole_error_contour} shows the absolute error of $\sigma_{xx}$ with the same mesh. As can be seen, the projection methods reduce error to an acceptable level (less than $.1\%$ of the maximal $\sigma_{xx}$) while the error the $Q_4$ element is at the same level of the maximal $\sigma_{xx}$. Here we can also see that the non-symmetric method has a slight improvement compared to the symmetric method.}
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.31\linewidth]{deformation_p_2} & \includegraphics[width=.31\linewidth]{deformation_p_3} & \includegraphics[width=.31\linewidth]{deformation_p_4}\\
\includegraphics[width=.31\linewidth]{stress_p_2} & \includegraphics[width=.31\linewidth]{stress_p_3} & \includegraphics[width=.31\linewidth]{stress_p_4}\\
\includegraphics[width=.31\linewidth]{energy_p_2} & \includegraphics[width=.31\linewidth]{energy_p_3} & \includegraphics[width=.31\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}

\begin{figure}[htb!]
    \center
    \begin{tabular}{cc}
    \includegraphics[width=.4\linewidth]{no_stress_contour} & \includegraphics[width=.4\linewidth]{g_stress_contour}\\
    $Q_4$ & $\mathcal{T}^{L^2} Q_4/Q_3$\\
    \includegraphics[width=.4\linewidth]{s_stress_contour} & \includegraphics[width=.4\linewidth]{ns_stress_contour}\\
    $S-\mathcal{T}^{p} Q_4/Q_3$ & $NS-\mathcal{T}^{p} Q_4/Q_3$\\
    \includegraphics[width=.4\linewidth]{reference_stress_contour} & \includegraphics[width=.14\linewidth]{legend}\\
    Reference & Legend
    \end{tabular}
        \caption{ Contour plots of $\sigma_{xx}^h$ for the plate with a circular hole ($p=4$, and the finest mesh is used).}
        \label{fig:platewithhole_contour}
\end{figure}

\begin{figure}[htb!]
    \center
    \begin{tabular}{cc}
    \includegraphics[width=.44\linewidth]{no} & \includegraphics[width=.5\linewidth]{g}\\
    $Q_4$ & $\mathcal{T}^{L^2} Q_4/Q_3$\\
    \includegraphics[width=.5\linewidth]{s} & \includegraphics[width=.5\linewidth]{ns}\\
    $S-\mathcal{T}^{p} Q_4/Q_3$ & $NS-\mathcal{T}^{p} Q_4/Q_3$
    \end{tabular}
        \caption{{\color{red} Can we change this to relative error?} Contour plots of $\vert{\sigma_{xx}-\sigma_{xx}^h}\vert$ for the plate with a circular hole ($p=4$, and the finest mesh is used).}
        \label{fig:platewithhole_error_contour}
\end{figure}
\section{Conclusions}
\label{sec:conclusion}

>>>>

\added{Contour plots of  $\sigma_{xx}$ for biquartic elements of the finest mesh are shown in Figure \ref{fig:platewithhole_contour}. We note that, for the finest mesh, results from all $\bar{B}$ methods are consistent with the reference solution, while using standard finite element results in large errors in the stress. Figure \ref{fig:platewithhole_error_contour} shows the absolute error of $\sigma_{xx}$ with the same mesh. As can be seen, the projection methods reduce error to an acceptable level (less than $.1\%$ of the maximal $\sigma_{xx}$) while the error the $Q_4$ element is at the same level of the maximal $\sigma_{xx}$. Here we can also see that the non-symmetric method has a slight improvement compared to the symmetric method.}
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.31\linewidth]{deformation_p_2} & \includegraphics[width=.31\linewidth]{deformation_p_3} & \includegraphics[width=.31\linewidth]{deformation_p_4}\\
\includegraphics[width=.31\linewidth]{stress_p_2} & \includegraphics[width=.31\linewidth]{stress_p_3} & \includegraphics[width=.31\linewidth]{stress_p_4}\\
\includegraphics[width=.31\linewidth]{energy_p_2} & \includegraphics[width=.31\linewidth]{energy_p_3} & \includegraphics[width=.31\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}

\begin{figure}[htb!]
    \center
    \begin{tabular}{cc}
    \includegraphics[width=.4\linewidth]{no_stress_contour} & \includegraphics[width=.4\linewidth]{g_stress_contour}\\
    $Q_4$ & $\mathcal{T}^{L^2} Q_4/Q_3$\\
    \includegraphics[width=.4\linewidth]{s_stress_contour} & \includegraphics[width=.4\linewidth]{ns_stress_contour}\\
    $S-\mathcal{T}^{p} Q_4/Q_3$ & $NS-\mathcal{T}^{p} Q_4/Q_3$\\
    \includegraphics[width=.4\linewidth]{reference_stress_contour} & \includegraphics[width=.14\linewidth]{legend}\\
    Reference & Legend
    \end{tabular}
        \caption{ Contour plots of $\sigma_{xx}^h$ for the plate with a circular hole ($p=4$, and the finest mesh is used). For reference the analytical solution is also plotted. }
        \label{fig:platewithhole_contour}
\end{figure}

\begin{figure}[htb!]
    \center
    \begin{tabular}{cc}
    \includegraphics[width=.44\linewidth]{no} & \includegraphics[width=.5\linewidth]{g}\\
    $Q_4$ & $\mathcal{T}^{L^2} Q_4/Q_3$\\
    \includegraphics[width=.5\linewidth]{s} & \includegraphics[width=.5\linewidth]{ns}\\
    $S-\mathcal{T}^{p} Q_4/Q_3$ & $NS-\mathcal{T}^{p} Q_4/Q_3$
    \end{tabular}
        \caption{Contour plots of $\vert{\sigma_{xx}-\sigma_{xx}^h}\vert$ for the plate with a circular hole ($p=4$, and the finest mesh is used).}
        \label{fig:platewithhole_error_contour}
\end{figure}
\section{Conclusions}
\label{sec:conclusion}
